A recipe for extremely reproducible enrichment analysis

### 2023-03-05 example.Rmd
big update

---
title: "Enrichment analysis with gold standard reproducibility."
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 7
theme: cosmo
---

@@

* "Recipes for extremely reproducible enrichment analysis"

@@

suppressPackageStartupMessages({
  library("getDEE2")
  library("DESeq2")
  library("kableExtra")
  library("vioplot")
  library("clusterProfiler")
  library("eulerr")
})

>>>>

---
title: "An example of extremely reproducible enrichment analysis."
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 7
theme: cosmo
---

@@

@@

suppressPackageStartupMessages({
  library("getDEE2")
  library("DESeq2")
  library("kableExtra")
  library("clusterProfiler")
  library("eulerr")
})

### 2023-03-05 manuscript.Rmd
big update

---
title: "Enrichment analysis with gold standard reproducibility"
author: "Mark Ziemann and Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

>>>>

---
title: "A recipe for extremely reproducible enrichment analysis"
Enrichment analysis with gold standard reproducibility"
author: "Mark Ziemann and Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

* "Enrichment analysis with gold standard reproducibility"
